### 2017-12-13 submission/manuscript.tex
change title

\section{What the Taq? The Influence of Different Hi-Fidelity Taq
Polymerase on 16S rRNA
Sequencing}\label{what-the-taq-the-influence-of-different-hi-fidelity-taq-polymerase-on-16s-rrna-sequencing}

>>>>

\section{What the Taq? The Influence of Different Hi-Fidelity Taq
Polymerase on 16S rRNA Gene
Sequencing}\label{what-the-taq-the-influence-of-different-hi-fidelity-taq-polymerase-on-16s-rrna-gene-sequencing}
